Efficient Machine Learning in a Memristor Network

### 2025-04-11 paper/paper.tex
Result regression for lemgth

Applications of PNN have been explored in fields ranging from optics\cite{}, to electronics\cite{}
and to fluidic and mecanical systems\cite{}, amongs others.

% ## Our networks and our algorithm ##

Not only, but physical neural networks make the similarity with the human brain more evident, opening the doors to the development of an artificial brain. For this, we choose to work with networks whose constructing elements are memristors living in aqueous solution and that respond to electrical, chemical and mechanical stimuli at the same time.

Fluidic channels are emerging as a promising technology in the field of neuromorphic computing due to their ability to emulate synaptic functions. These nanoscale devices can store information through conductance changes. Their unique properties make them suitable for implementing artificial neural networks and other types of electrical networks.

In recent years, machine learning algorithms have increasingly been applied to memristor networks to train specific input-output relations. These algorithms typically modify the dynamics of the memristors to achieve desired computational tasks.

@@

The paper is roganized as follows. Section 2 reviews related work on memristor networks, machine learning algorithms, and physical learning methods. Section 3 describes the methods used in our study, including the network model, machine learning algorithm, and the physical learning approach. In Section 4, we present our proposed method for coupling memristors with capacitors and discuss the necessary properties for effective training. Section 5 details our experimental setup and implementation. The results and analysis are provided in Section 6, followed by conclusions and suggestions for future work in Section 7.

@@

To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies. Reaching a desired input-output voltage mapping in a generic electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{plots/general_network/mse_general.pdf}
    \caption{Network to the right has inputs $[5,0]$ and desired outputs $[3, 4]$, delta weights a third of their intial value and learning rates $1e^{-5}, 1e^{-4}, 1e^{2}$. The network to the right has $[5,1,0]$ and output $[3,4,2]$}\label{fig:mse_general}
\end{figure}

\cleardoublepage
\subsection{Linear Regression}

@@

The training algorithm presented in \cref{sec:training} can be slightly adapted to function for this training objective. At each step of the training, a pair of input and output voltages is selected from the training set, and used as input voltage and desired output in the algorithm above. In order to evaluate how well the algorithm is performing, the testset is evaluated at every step of the training by computing the test cost function. If the trained weight set after certain training step is $\boldsymbol{w}$, we define this function as
\[
C_{t}\left( \boldsymbol{w} \right) = \sum_{j=1}^{Te}\brac{V_{out}\brac{\boldsymbol{w}} - V_j^D}^2,
\]
which considers the difference between the voltage measured in the output node when the impoing the $j-$th input voltage of the test set and the desired output of the same test point, for every point of the set.

>>>>

Applications of PNNs have been explored across diverse fields, including optics \cite{optics1}, electronics \cite{electronics1}, and fluidic and mechanical systems \cite{}, among others. Many existing training algorithms rely entirely on in silico methods, which often face challenges when transferring the learned model to real physical devices. To address this, hybrid training approaches have been proposed, where the inference phase is executed physically while the backward phase is computed numerically. Other methods, based on coupled learning, implement local learning rules at the level of each connection or edge. However, these approaches still face the need for two identical physical systems to apply different boundary conditions. In this work, we propose a novel algorithm in which both inference and backpropagation are carried out through physical processes, specifically leveraging the natural relaxation dynamics of the system in response to external stimuli and weight modifications.

A key advantage of PNNs is their ability to more closely emulate certain functional aspects of biological neural systems. One of the defining features of the brain is its capacity to process and integrate multiple types of stimuli—such as electrical, chemical, and mechanical inputs—simultaneously. This multimodal responsiveness is believed to contribute significantly to the brain’s efficiency and adaptability \cite{}. Inspired by this, we focus on neural networks constructed from memristive elements. Specifically, we utilize ionic microfluidic channels in aqueous solutions\cite{Rene_IonicNeuromorphic}, which exhibit the unique ability to respond concurrently to diverse physical stimuli. This characteristic is central to the operation of our proposed training algorithm.

@@

The paper is organized as follows. Section 2 reviews related work on memristor networks, machine learning algorithms, and physical learning methods. Section 3 describes the methods used in our study, including the network model, machine learning algorithm, and the physical learning approach. In Section 4, we present our proposed method for coupling memristors with capacitors and discuss the necessary properties for effective training. Section 5 details our experimental setup and implementation. The results and analysis are provided in Section 6, followed by conclusions and suggestions for future work in Section 7.

@@

To generalize the training objective to a more general objective, we consider memrisotr network built from a bigger network geometry. \cref{fig:mse_general}(a) shows a three-input and two-output network, that we train to give $[3V, 4V]$ in the output nudes, when $[0V, 2V, 5V]$ are given as input. Reaching a desired input-output voltage mapping in a generic electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses. [...]

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/general_network/mse_general.pdf}
    \caption{(a) Generic network with $9$ nodes and $15$ edges with inputs $[V_{2}, V_{4}, V_{9}] = [0V, 2V, 5V]$ and desired outputs $[V_{5}^D, V_{7}^D] = [3V, 4V]$, delta weights a third of their intial value and learning rates $[0.001, 1, 0.0001, 0.001]$. (b) Cost funtion during training of generic graph for input-output mapping task. The different colors indicate different weight choise.}\label{fig:mse_general}
\end{figure}

The result of the training is presented in \cref{fig:mse_general}(b), which shows how the cost function responds to the wieght updates performed in the algorithm, for each of the four different weights. All of the possible different choices of weight result in a trained set that decreases the initial error of many orders of magnitudes.

% \cleardoublepage
\subsection{Linear Regression}

@@

The training algorithm presented in \cref{sec:training} can be slightly adapted to function for this training objective. At each step of the training, a pair of input and output voltages is selected from the training set, and used as input voltage and desired output in the algorithm above. In order to evaluate how well the algorithm is performing, the testset is evaluated by computing the test cost function. If the trained weight set after certain training step is $\boldsymbol{w}$, we define this function as
\[
C_{t}\left( \boldsymbol{w} \right) = \sum_{j=1}^{Te}\brac{V_{out}\brac{\boldsymbol{w}} - V_j^D}^2,
\]
which considers the difference between the voltage measured in the output node when the impoing the $j-$th input voltage of the test set and the desired output of the same test point, for every point of the set.
